Adaptive broadcast tree for multicores

### 2013-04-29 paper.tex
Mentioned send and receive cost in model + table of simulation results

\subsubsection{Example model approximating a 8x4x1 machine}

@@

@@

>>>>

\subsubsection{Example model approximating a 8x4x1 machine}
\label{sec:example_model}

@@

Send and receive time are $10$ each, i.e.\ in the order of propagation
over a cross-NUMA link.

@@

\subsection{Simulation in model}

This section shows results for a simulation based on the model
introduced in Section~\ref{sec:example_model}

The time given is a fictional time unit at this point.

\begin{table}[htb]
  \centering
  \begin{tabular}{llll}
    \toprule
    overlay & scheduling & time & factor \\
    \midrule
    MST & naive         & 241 & 1.00 \\
    MST & longest first & 151 & 0.63 \\
    \bottomrule
  \end{tabular}
  \caption{Simulation results for simplified machine model}
  \label{tab:sim_results}
\end{table}

\subsection{Real hardware}
